\documentclass[12pt]{article}
\usepackage[a4paper,margin=18mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{tabularx}

\setlength{\parindent}{0pt}
\pagestyle{empty}

\newcommand{\checkbox}{\(\square\)}
\newcommand{\formsection}[1]{%
  \vspace{0.65em}\noindent{\large\bfseries #1}\par\vspace{0.35em}}
\newcommand{\fieldline}[1]{\textbf{#1}\ \hrulefill}

\begin{document}

\begin{center}
  {\LARGE\bfseries Project-StarFall Code Quality Assurance Record}\\[0.25em]
  {\large Cover Sheet}
\end{center}

The questioner completes one cover sheet for each pull request and attaches
one or more copies of \texttt{qa\_sup.pdf} to record the questions and
evaluations.

\begin{enumerate}[leftmargin=*,itemsep=0.15em,topsep=0.4em]
  \item The questioner must print the form and complete it by hand in ink.
  \item Conduct the QA live using Zoom or another real-time meeting platform.
        The PR author must answer each question live and without AI assistance,
        and must not access or complete this record.
  \item The questioner must be the next technical authority: Component
        Maintainer for a Contributor, Family Maintainer for a Component
        Maintainer, Project Maintainer for a Family Maintainer, or a different
        qualified Family Maintainer for the Project Maintainer.
  \item The questioner must keep the original for four months after merge,
        unless it is sent earlier at the Project Maintainer's request. During
        the first three months after merge, the Project Maintainer may request
        delivery. The request must provide the address and required delivery
        service, and the Hotaru maintenance team will cover the delivery fee.
        Without such a request, no delivery is required. Failure to retain or
        produce a requested original may cause the declaration to be treated
        as unverified or potentially false and referred for governance review.
  \item Write in English, Japanese, Traditional Chinese, or Simplified Chinese.
\end{enumerate}

\formsection{I. Pull request details}

\begin{tabularx}{\textwidth}{@{}lX@{\hspace{1.5em}}lX@{}}
  \textbf{Repository:} & \hrulefill &
  \textbf{PR number:} & \hrulefill \\[0.9em]
\end{tabularx}

\begin{tabularx}{\textwidth}{@{}lX@{\hspace{1.5em}}lX@{}}
  \textbf{PR author:} & \hrulefill & \textbf{Date:} & \hrulefill \\[0.9em]
  \textbf{Family:} & \hrulefill & \textbf{Component:} & \hrulefill \\[0.9em]
  \textbf{Questioner:} & \hrulefill & \textbf{Pages attached:} & \hrulefill
\end{tabularx}

\formsection{II. Review conditions}

Mark every statement that applies.

\begin{itemize}[label={},leftmargin=0pt,itemsep=0.25em,topsep=0.35em]
  \item \checkbox\ The questioner is the responsible Component, Family, or
        Project Maintainer.
  \item \checkbox\ The questioner did not author the code being reviewed.
  \item \checkbox\ The change introduces or alters a public module, type,
        trait, function, or other stable API.
  \item \checkbox\ The PR author's completed Update Report has been received.
\end{itemize}

\textbf{PR's declared AI tier:}\quad
\checkbox\ Forbidden \quad
\checkbox\ Author-Owned \quad
\checkbox\ Human-Led \quad
\checkbox\ Co-Authored

\formsection{III. Declarations}

\textbf{Questioner declaration.} I conducted this QA live with the PR author
using a real-time meeting platform. I reviewed and understand the code covered
by this record and accept responsibility for the accuracy of my evaluation. I
accurately recorded the questions, my evaluations, and any supplementary
clarification. The PR author answered every recorded question live and without
AI assistance, and did not access or complete this document. I completed this
record, including every attached page, by hand in ink and without AI
assistance.

\vspace{0.75em}
\fieldline{Questioner signature:}
\hspace{1.5em}
\fieldline{Date:}

\vfill
\begin{center}
  \small Page 1 of \underline{\hspace{1.3cm}}
\end{center}

\end{document}
