\documentclass[12pt]{article}
\usepackage[a4paper,margin=18mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{tabularx}

\setlength{\parindent}{0pt}
\pagestyle{empty}

\newcommand{\checkbox}{\(\square\)}
\newcommand{\formsection}[1]{%
  \vspace{0.65em}\noindent{\large\bfseries #1}\par\vspace{0.35em}}
\newcommand{\fieldline}[1]{\textbf{#1}\ \hrulefill}

\begin{document}

\begin{center}
  {\LARGE\bfseries Project-StarFall Code Update Report}\\[0.25em]
  {\large Cover Sheet}
\end{center}

Complete one cover sheet for each pull request. Attach as many copies of
\texttt{report\_sup.pdf} as needed to record its distinct changes. For a
redesign, use the justification field to compare the proposed approach with the
previous approach.

\begin{enumerate}[leftmargin=*,itemsep=0.15em,topsep=0.4em]
  \item Print the form and complete it by hand in ink.
  \item Submit it to the next technical authority with the pull request:
        Contributor to Component Maintainer, Component Maintainer to Family
        Maintainer, Family Maintainer to Project Maintainer, and Project
        Maintainer to a different qualified Family Maintainer.
  \item The PR author must keep the original for four months after merge,
        unless it is sent earlier at the Project Maintainer's request. During
        the first three months after merge, the Project Maintainer may request
        delivery. The request must provide the address and required delivery
        service, and the Hotaru maintenance team will cover the delivery fee.
        Without such a request, no delivery is required. Failure to retain or
        produce a requested original may cause the declaration to be treated
        as unverified or potentially false and referred for governance review.
  \item Write in English, Japanese, Traditional Chinese, or Simplified Chinese.
\end{enumerate}

\formsection{I. Pull request details}

\begin{tabularx}{\textwidth}{@{}lX@{\hspace{1.5em}}lX@{}}
  \textbf{Repository:} & \hrulefill &
  \textbf{PR number:} & \hrulefill \\[0.9em]
\end{tabularx}

\begin{tabularx}{\textwidth}{@{}lX@{\hspace{1.5em}}lX@{}}
  \textbf{PR author:} & \hrulefill & \textbf{Date:} & \hrulefill \\[0.9em]
  \textbf{Family:} & \hrulefill & \textbf{Component:} & \hrulefill \\[0.9em]
  \textbf{Submitted to:} & \hrulefill & \textbf{Detail pages:} & \hrulefill
\end{tabularx}

\formsection{II. Submission details}

\textbf{Role:}\quad
\checkbox\ Contributor \quad
\checkbox\ Component Maintainer \quad
\checkbox\ Family Maintainer

\vspace{0.45em}
\textbf{PR's declared AI tier:}\quad
\checkbox\ Forbidden \quad
\checkbox\ Author-Owned \quad
\checkbox\ Human-Led \quad
\checkbox\ Co-Authored

\vspace{0.45em}
\textbf{AI assistance used in this PR:}\quad
\checkbox\ No \quad
\checkbox\ Yes

\quad If yes: \checkbox\ Design \quad \checkbox\ Code \quad
\checkbox\ Tests \quad \checkbox\ Documentation

\formsection{III. PR author declaration}

I have personally reviewed and understand every submitted change, and I accept
responsibility for the code covered by this report. The attached detail pages
identify the affected code, the design used, and why that design should be
adopted. I can explain, modify, test, and debug the work without asking an AI
system to reconstruct it for me.

\vspace{0.5em}
I completed this report, including every attached page, by hand in ink and
without AI assistance. The AI disclosure above applies only to work on the
pull request.

\vspace{1em}
\fieldline{PR author signature:}
\hspace{1.5em}
\fieldline{Date:}

\vfill
\begin{center}
  \small Page 1 of \underline{\hspace{1.3cm}}
\end{center}

\end{document}
